---
title: "CITS5551 - Group3"
author: "Data Analysis"
output: html_notebook
---

### Introduction
My data comes from Kaggle. License is Public Domain.https://www.kaggle.com/datasets/arshid/iris-flower-dataset?select=IRIS.csv
The Iris flower data set is a multivariate data set introduced by the British statistician and biologist Ronald Fisher in his 1936 paper The use of multiple measurements in taxonomic problems. It is sometimes called Anderson's Iris data set because Edgar Anderson collected the data to quantify the morphologic variation of Iris flowers of three related species. The data set consists of 50 samples from each of three species of Iris (Iris Setosa, Iris virginica, and Iris versicolor). Four features were measured from each sample: the length and the width of the sepals and petals, in centimeters.


### Data loading, full setup, and overall database data
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(hexbin)
library(party)
library(rpart)
library(rpart.plot)
library(tidyverse)
library(skimr)
library(DataExplorer)
library(pROC)
library(tidyverse)
library(randomForest)
library(caret)
library(e1071)
library(fpc)
```
Load the original database:
```{r}
IRIS <-read.csv("/Users/ame/OneDrive/AME 2022 SEMESTER 1/CITS5551/Project/IRIS.csv")
IRIS
```

Analyze the data with str( ):
```{r}
str(IRIS)
```

Analyze the data with head( ):
```{r}
head(IRIS)
```

Count the number of NA for each classification:
```{r}
apply(is.na(IRIS), 2, sum)
```

#### All data transformations are done separately in each Topic, including data cleansing
### [1]Topic of sepal

Data cleaning and creation:
```{r}
sepal <-subset(IRIS,select=c(sepal_length,sepal_width,species))   
sepal
ggplot(sepal,aes(x=sepal_length,y=sepal_width,color=species),)+geom_point()+ggtitle("") 
ggplot(sepal,aes(x=sepal_length,y=sepal_width,color=species,fill="white"))+geom_violin(fill="steelblue",alpha=.6)+ggtitle("")
```
### [2]Topic of petal

Data cleaning and creation:
```{r}
petal <-subset(IRIS,select=c(petal_length,petal_width,species)) 
petal
ggplot(petal,aes(x=petal_length,y=petal_width,color=species),)+geom_point()+ggtitle("") 

ggplot(petal,aes(x=petal_length,y=petal_width,color=species,fill="white"))+geom_violin(fill="steelblue",alpha=.6)+ggtitle("")
```

```{r}
data1 <- na.omit(IRIS)
plot_missing(data1)     #Show missing values
data1$species<- factor(data1$species)     #Convert numeric category to factor category
skim(data1)            #Skim data after data processing
table(data1$species)    #Distribution of dependent variables
   

#The set. Seed() function is used to ensure that the random numbers you randomly generate are consistent
trains <- createDataPartition(
  y= data1$species,
  p=0.7,
  list= F
  
)
traindata <- data1[trains,]     #70% training data      
testdata <- data1[-trains,]     #30% testing data
#Distribution of dependent variables after splitting
table(traindata$species)   
table(testdata$species)   
colnames(data1)

#Dependent variable and independent variable construction formula:
form_clsm <- as.formula(
  paste0(
    "species ~ ",
    paste(colnames(traindata)[1:4],collapse = " + ")
  )
)
#Building decision tree model
set.seed(35)
fit_dt_clsm <- rpart(
  form_clsm,
  data = traindata,
  method = "anova",
  parms = list(split = "information"),
  control = rpart.control(cp=0.005) 
  )
#Complexity related data
printcp(fit_dt_clsm)
plotcp(fit_dt_clsm)
#post-pruning
fit_dt_clsm_pruned <- prune(fit_dt_clsm, cp = 0.0016)
#Variable importance
fit_dt_clsm_pruned$variable.importance
varimpdata <- data.frame(importance = fit_dt_clsm_pruned$variable.importance)
varimpdata 
#Drawing
ggplot(varimpdata,aes(x = as_factor(rownames(varimpdata)),y= importance))+geom_col() + labs(x= "variables")+ theme(axis.text.x = element_text(angle = 15,hjust = 1))+ theme_classic()
```
### Conclusion
We have completed the overview of CSV files, data cleaning, data analysis, data visualization, and variable importance analysis.

